---
title: "Sampling"
---

Follow along with the demo to learn how to sample data from a population using R and the Tidyverse. You should get started by loading the tidyverse in a new R block.

### Task 1: Load the tidyverse
```{r}
library(tidyverse)
```

### Task 2: Load 1,000 rows of data with the ages of people from 18-80
```{r}
set.seed(42)

population <- tibble(
  age = sample(18:80, 1000, replace = TRUE)
)

population
```

### Task 3: Sample 100 rows of data from the dataset
```{r}
sampled_data <- population |> 
  slice_sample(n = 20)

sampled_data
```

### Task 4: Calculate the mean age and standard deviation of the sample
```{r}
sample_stats <- sampled_data |> 
  summarise(
    mean_age = mean(age),
    sd_age   = sd(age)
  )

sample_stats
```

### Task 5: Calculate the mean age and standard deviation of the population
```{r}
population_stats <- population |> 
  summarise(
    mean_age = mean(age),
    sd_age   = sd(age)
  )

population_stats
```

### Task 6: Compare the sample and population statistics
```{r}
comparison <- bind_rows(
  sample_stats     |> mutate(source = "Sample (n=100)"),
  population_stats |> mutate(source = "Population (n=1000)")
) |> 
  select(source, mean_age, sd_age)

comparison
```

Compare the means and standard deviations. Are they similar? Go back and re-run the sampling and statistics calculations with a smaller sample size. How do the results change?

The mean and standard deviation are extremely similar to each other at n=100 and n=1000

With a sample size of 100, the sample mean and standard deviation should be fairly close to the population values. Try dropping the sample to 10 or 20 rows — you'll notice the mean can drift noticeably from the population mean and the standard deviation becomes less stable. This illustrates how larger samples produce more reliable estimates of population parameters.

Even at 10 or 20 rows, actually, the mean and standard deviation remain remarkably consistent.


```{r}
comparison <- bind_rows(
  sample_stats     |> mutate(source = "Sample (n=20)"),
  population_stats |> mutate(source = "Population (n=1000)")
) |> 
  select(source, mean_age, sd_age)

comparison
```
When finished, save your work, switch to GitHub Desktop, then add, commit and push your changes to GitHub and submit the URL of the notebook in ELMS.
